Grade Retention and Mixed Race

### 2022-09-09 products/paper/main.qmd
Update captions in paper

```{r fig-black-models}
#| label: fig-black-models
#| fig-pos: p
#| fig-cap: Probability of being behind grade for biracial respondents with one black parent, in comparison to their monoracial comparison groups. 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level, Baseline model includes year, grade, location, and state fixed effects. Full models include control variables for nativity, English proficiency, income, education, home ownership, and marital status of parents.
#| fig-height: 7.3
coef_table %>%
  filter(model=="Baseline model" | model=="Full model") %>%
  filter(str_detect(mrace, "Black")) %>%
  ggplot(aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower, ymax=upper, fill=colors), 
            color=NA, alpha=0.5)+
  geom_linerange(data=subset(ci_df, 
                             (model=="Baseline model" |  model=="Full model") &
                               str_detect(mrace, "Black")), 
                 position=position_dodge2(width = 0.1), size=1, alpha=0.5,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=color_choices)+
  scale_fill_manual(values=color_choices)+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average predicted probability of being clearly behind expected grade")
```

@@

```{r fig-other-models}
#| label: fig-other-models
#| fig-pos: p
#| fig-cap: Probability of being behind grade for non-black biracial respondents, in comparison to their monoracial comparison groups. 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level, Baseline model includes year, grade, location, and state fixed effects. Full models include control variables for nativity, English proficiency, income, education, home ownership, and marital status of parents.
#| fig-height: 7.3
coef_table %>%
  filter(model=="Baseline model" | model=="Full model") %>%
  filter(!str_detect(mrace, "Black")) %>%
  ggplot(aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower, ymax=upper, fill=colors), 
            color=NA, alpha=0.5)+
  geom_linerange(data=subset(ci_df, 
                             (model=="Baseline model" | model=="Full model") &
                               !str_detect(mrace, "Black")), 
                 position=position_dodge2(width = 0.1), size=1, alpha=0.5,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=color_choices[-1])+
  scale_fill_manual(values=color_choices[-1])+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average predicted probability of being clearly behind expected grade")
```

>>>>

```{r fig-black-models}
#| label: fig-black-models
#| fig-pos: p
#| fig-cap: Probability of being behind grade for biracial respondents with one black parent, in comparison to their monoracial comparison groups. . Non-overlap in color corresponding confidence bands indicates statistically significant difference at the 5% level, Baseline model includes year, grade, location, and state fixed effects. Full models include control variables for nativity, English proficiency, income, education, home ownership, and marital status of parents.
#| fig-height: 7.3
coef_table %>%
  filter(model=="Baseline model" | model=="Full model") %>%
  filter(str_detect(mrace, "Black")) %>%
  ggplot(aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower, ymax=upper, fill=colors), 
            color=NA, alpha=0.5)+
  geom_linerange(data=subset(ci_df, 
                             (model=="Baseline model" |  model=="Full model") &
                               str_detect(mrace, "Black")), 
                 position=position_dodge2(width = 0.1), size=1, alpha=0.5,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=color_choices)+
  scale_fill_manual(values=color_choices)+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average predicted probability of being clearly behind expected grade")
```

@@

```{r fig-other-models}
#| label: fig-other-models
#| fig-pos: p
#| fig-cap: Probability of being behind grade for non-black biracial respondents, in comparison to their monoracial comparison groups. Non-overlap in color corresponding confidence bands indicates statistically significant difference at the 5% level, Baseline model includes year, grade, location, and state fixed effects. Full models include control variables for nativity, English proficiency, income, education, home ownership, and marital status of parents.
#| fig-height: 7.3
coef_table %>%
  filter(model=="Baseline model" | model=="Full model") %>%
  filter(!str_detect(mrace, "Black")) %>%
  ggplot(aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower, ymax=upper, fill=colors), 
            color=NA, alpha=0.5)+
  geom_linerange(data=subset(ci_df, 
                             (model=="Baseline model" | model=="Full model") &
                               !str_detect(mrace, "Black")), 
                 position=position_dodge2(width = 0.1), size=1, alpha=0.5,
                 aes(ymin=lower, ymax=upper, color=colors))+
  geom_point()+
  coord_flip()+
  facet_grid(mrace~model, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=color_choices[-1])+
  scale_fill_manual(values=color_choices[-1])+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average predicted probability of being clearly behind expected grade")
```
